---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
library(magick)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Rubik:ital,wght@0,300..900;1,300..900&display=swap');

body {
  background-color: #25262E;
  color: #E9E9E9;
}

h1, h2, h3 {
  text-align: center;
}

h1 {
  font-weight: 700;
  margin-bottom: 20px;
  font-size: 100px !important;
  letter-spacing: 4px;
  font-family: 'Bebas Neue';
}

h2, h3 {
  font-family: "Rubik", sans-serif;
  font-size: 50px;
  font-weight: 700;
}

p {
  font-size: 20px;
  font-family: "Rubik", sans-serif;
}

img {
  border: 5px solid #404040;
}

ul {
  font-family: "Rubik", sans-serif;
  text-align: left;
}

div {
  text-align: center;
}
```

## Analysing My YouTube Viewing Habits

This report analyses my personal YouTube viewing habits based on tracked data over the past week. The data was collected by manually logging each video I watched, including information about:

- Video categories (some videos may belong to multiple categories)
- How I discovered each video
- My enjoyment rating (scale of 1-10)
- When I watched the video
- The length of each video in minutes

```{r}
# Reading CSV data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSBvWeoajBgTZ_JLkowqy5_j4VMGj0l6JjPTL9LtB1vRjQgFvIeVBNUMscVXEOFffUA3uNZwBboVTm-/pub?output=csv")

# Renaming columns 
latest_data <- logged_data %>%
  rename(
    video_length = 2,
    categories = 3,
    discovery_method = 4,
    time_watched = 5,
    rating = 6
  )

# Calculate summaries
mean_video_length <- mean(latest_data$video_length, na.rm = TRUE)
mean_rating <- mean(latest_data$rating, na.rm = TRUE)
total_videos <- nrow(latest_data)
```

### Most Watched Categories

The chart below shows the distribution of video categories in my viewing history. This identifies the categories I watch most.

```{r}
# Creating Category Bar Chart
latest_data %>%
  separate_rows(categories, sep = ", ") %>%
  count(categories) %>%
  ggplot(aes(y = reorder(categories, n), x = n)) +
  geom_col(fill = "#FF0000") +
  labs(title = "Distribution of YouTube Video Categories Watched", 
       x = "Number of Videos", 
       y = NULL) +
  theme_minimal()
```



Based on my viewing data, I've watched a total of **`r total_videos`** videos across the past week. The chart reveals that **`r latest_data %>% separate_rows(categories, sep = ", ") %>% count(categories) %>% arrange(desc(n)) %>% slice(1) %>% pull(categories)`** is my most frequently watched category, closely followed by **`r latest_data %>% separate_rows(categories, sep = ", ") %>% count(categories) %>% arrange(desc(n)) %>% slice(2) %>% pull(categories)`** and **`r latest_data %>% separate_rows(categories, sep = ", ") %>% count(categories) %>% arrange(desc(n)) %>% slice(3) %>% pull(categories)`**.

### How I Discover Videos

This visualization shows the different ways I discover videos on YouTube, which provides insight into my browsing habits.

```{r}
# Creating Discovery Bar Chart
latest_data %>%
  count(discovery_method) %>%
  ggplot(aes(x = reorder(discovery_method, n), y = n)) +
  geom_col(fill = "#FF0000") +
  labs(title = "How I Discover YouTube Videos", 
       x = NULL, 
       y = "Number of Videos") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

By a large margin, videos **`r latest_data %>% count(discovery_method) %>% arrange(desc(n)) %>% slice(1) %>% pull(discovery_method)`** is the most common way I discover YouTube videos, which accounts for **`r round(100 * (latest_data %>% count(discovery_method) %>% arrange(desc(n)) %>% slice(1) %>% pull(n) / total_videos), 1)`%** of my video discoveries.

### Video Length and Engagement

```{r}
# Calculate additional stats
max_rating <- max(latest_data$rating, na.rm = TRUE)
min_rating <- min(latest_data$rating, na.rm = TRUE)
```

The average length of videos I watch is **`r ifelse(mean_video_length < 16, paste(round(mean_video_length, 1), "minutes. This suggests I tend to enjoy shorter content on YouTube."), paste(round(mean_video_length, 1), "minutes. This suggests I tend to prefer longer content on YouTube"))`**.

My average rating for the videos I watch is **`r ifelse(mean_rating < 6, paste(round(mean_rating, 1), "out of 10. This suggests I am typically not satisfied with the content I choose to watch."), paste(round(mean_rating, 1), "out of 10. This implies I am generally satisfied with the content I watch"))`**.

### Mean Engagement Levels by Discovery Method

```{r}
# Calculate mean engagement level for each discovery method
mean_engagement_by_method <- latest_data %>%
  group_by(discovery_method) %>%
  summarise(mean_rating = mean(rating, na.rm = TRUE)) %>%
  arrange(desc(mean_rating))
```

The plot below summarizes the average engagement level (rating) for each discovery method. This helps to understand whether my satisfaction with the videos correlates with how I discovered them.

```{r}
# Creating a Bar Chart for Mean Engagement by Discovery Method
mean_engagement_by_method %>%
  ggplot(aes(x = reorder(discovery_method, mean_rating), y = mean_rating)) +
  geom_col(fill = "#FF0000") +
  labs(title = "Average Engagement by Discovery Method", 
       x = "Discovery Method", 
       y = "Average Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Average Ratings For Categories By Video Length

Below is a chart visualizing the average ratings of categories, grouped by video length. This gives insight in how ratings for categories vary across video lengths.

```{r}
# Creating Category-based Video Length Categories
latest_data <- latest_data %>%
  mutate(video_length_category = case_when(
    video_length < 10 ~ "Short (<10 min)",
    video_length >= 10 & video_length < 20 ~ "Medium (10-20 min)",
    video_length >= 20 ~ "Long (>20 min)"
  ))

# Function to generate the bar plot for a given video length category
generate_bar_plot <- function(length_category) {
  # Filter data for the current video length category
  length_data <- latest_data %>%
    separate_rows(categories, sep = ", ") %>%
    filter(video_length_category == length_category)
  
  # Calculate average rating by category for the length category
  avg_rating_length <- length_data %>%
    group_by(categories) %>%
    summarise(mean_rating = mean(rating, na.rm = TRUE))
  
  # Generate the plot
  plot <- ggplot(avg_rating_length, aes(x = reorder(categories, mean_rating), y = mean_rating)) +
    geom_col(fill = "#FF0000") +
    labs(title = paste("Average Rating by Category -", length_category, "Videos"),
         x = "Category", y = "Average Rating") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.background = element_rect(fill = "white", color = "white"))
  
  plot_file <- tempfile(fileext = ".png")
  ggsave(plot_file, plot, width = 8, height = 6, dpi = 100)
  
  return(plot_file)
}

# List of video length categories to loop through
length_categories <- c("Short (<10 min)", "Medium (10-20 min)", "Long (>20 min)")

# Generate a list of image files (saved plots) for each video length category
plot_files <- lapply(length_categories, function(category) {
  generate_bar_plot(category)
})

# Read the images into magick
frames <- lapply(plot_files, image_read)

# Animate the frames
animated_gif <- image_animate(image_join(frames), fps = 0.5)

# Display GIF
animated_gif
```

Based on the video length categories, we can see the following:

- *Short (<10 min)* videos tend to have an average rating of *`r latest_data %>% filter(video_length_category == "Short (<10 min)") %>% summarize(avg_rating = round(mean(rating, na.rm = TRUE), 2)) %>% pull(avg_rating)`*.
- *Medium (10-20 min)* videos show an average rating of *`r latest_data %>% filter(video_length_category == "Medium (10-20 min)") %>% summarize(avg_rating = round(mean(rating, na.rm = TRUE), 2)) %>% pull(avg_rating)`*.
- *Long (>20 min)* videos tend to have an average rating of *`r latest_data %>% filter(video_length_category == "Long (>20 min)") %>% summarize(avg_rating = round(mean(rating, na.rm = TRUE), 2)) %>% pull(avg_rating)`*.


